---
title: "Supplementary Data SD1"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
library(leaflet)
library(sf)
library(tidyverse)

```

```{r loading data , message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
all_layers <- sf::st_read("data/all_layers_simplified_interactive_map.shp")
# simplified in mapshaper (https://mapshaper.org) at 10%

# Fixing Iberá
all_layers[68,1] <- 'Iberá'
```

```{r}
title_var <- "Supplementary Data SD1"
# https://stackoverflow.com/questions/58188845/rmarkdown-tab-name-in-browser
```    

---
title: `r title_var`
---

<style>
  .title{
    display: none;
  }
</style>

```{r inicializo_mapa, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
interactive_map <- leaflet() %>%
  # addControl(title, position = "topleft", className="map-title") %>% 
  addProviderTiles("Esri.WorldGrayCanvas", options = tileOptions(minZoom=3, maxZoom=7)) %>% 
  addMapPane("int", zIndex = 450) %>%
  addMapPane("ar", zIndex = 410) %>%
  addMapPane("ctenomys", zIndex = 400) %>%
  addMapPane("ctenomys_lista", zIndex = 420) 
```

```{r ctenomys, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

ctenomys <- all_layers %>% 
  filter(capa == 'DA') %>% 
  mutate(BINOMIA = paste0('<i>',BINOMIA,'</i>')) 

ctenomys[68,1] <- 'Iberá'

ctenomys.lista <- split(ctenomys, ctenomys$BINOMIA)

names(ctenomys.lista) %>%
  purrr::walk( function(df) {
    interactive_map <<- interactive_map %>%
      addPolygons(color = '#1034A6',
                  data = ctenomys.lista[[df]],
                  options = pathOptions(pane = "ctenomys_lista"),
                  weight = 1,
                  smoothFactor = 0.5,
                  opacity = 0.8,
                  fillOpacity = 0.2,
                  fillColor = '#1034A6',
                  group = ctenomys.lista[[df]]$BINOMIA,
                  popup = paste0(ctenomys.lista[[df]]$BINOMIA,' - DA: ', ctenomys.lista[[df]]$ar_sn_g," km<sup>2</sup>"),
                  highlightOptions = highlightOptions(color = '#1034A6',
                                                      weight = 2,
                                                      bringToFront = TRUE))})
```


```{r ctenomys_todos, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

interactive_map <- interactive_map %>% 
  addPolygons(color = '#1034A6',
              data = ctenomys,
              options = pathOptions(pane = "ctenomys"),
              weight = 1,
              smoothFactor = 0.5,
              opacity = 0.8,
              fillOpacity = 0.1,
              fillColor = '#1034A6',
              popup = paste0(ctenomys$BINOMIA),
              group = paste0('<i> Ctenomys</i> Distribution areas'),
              highlightOptions = highlightOptions(color = '#1034A6',
                                                  weight = 2,
                                                  bringToFront = TRUE))
```

```{r PAs, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
areas <- all_layers %>% 
  filter(capa == 'PA')

interactive_map <- interactive_map %>% 
    addPolygons(color = '#eec900', #gold2
              data = areas,
              options = pathOptions(pane = "ar"),
              weight = 1,
              smoothFactor = 0.5,
              opacity = 0.8,
              fillOpacity = 0.1,
              fillColor = '#eec900',
              popup = areas$orig_name,
              group = 'Protected areas',
              highlightOptions = highlightOptions(color = '#eec900',
                                    weight = 2,
                                                  bringToFront = TRUE))
```

```{r Intersections, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

intersections <- all_layers %>% 
  filter(capa == 'I') %>% 
  mutate(BINOMIA = paste0('<i>',BINOMIA,'</i>'))

intersections[42,1] <- 'Iberá'

interactive_map <- interactive_map %>% 
  addPolygons(color = '#d26da3', #purple#551a8b
              data = intersections,
              options = pathOptions(pane = "int"),
              weight = 1,
              smoothFactor = 0.5,
              opacity = 0.8,
              fillOpacity = 0.5,
              fillColor = '#d26da3',
              popup = paste0(intersections$BINOMIA," - PA"),
              group = 'Intersections',
              highlightOptions = highlightOptions(color = '#d26da3',
                                                  weight = 2,
                                                  bringToFront = TRUE))

```


```{r legend, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

interactive_map <- interactive_map %>%
  addLegend("bottomleft",
            colors=c('#1034A6', '#eec900','#d26da3'),
            values = c('Distribution areas', 'Protected areas', 'Intersections'),
            labels= c('Distribution areas', 'Protected areas', 'Intersections'),
            # title = "Polygons",
            opacity = 1)

```

```{r Selector, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
interactive_map <- interactive_map %>%
    addLayersControl(overlayGroups = c('Protected areas', 'Intersections',paste0('<i> Ctenomys</i> Distribution areas'),names(ctenomys.lista)),
                   options = layersControlOptions(collapsed = T)
                   ) %>% 
  hideGroup(c('Protected areas','Intersections',paste0('<i> Ctenomys</i> Distribution areas'),names(ctenomys.lista)))
```

## "Filling the gap in distribution ranges and conservation status in *Ctenomys* (Rodentia: Ctenomyidae)."
### *Caraballo, D. A., López, S. L., Botero-Cañola, S., and Gardner S. L.*

#### **Supplementary Data SD1**. Interactive map showing _Ctenomys_ geographic distribution areas (DAs), protected areas (PAs), and their intersection.

The icon located at the upper right corner is an dropdown menu that allows to select/deselect layers of interest. By selecting a species layer, the name of the species and its total area of distribution are displayed after clicking. By clicking on a PA,  the name is shown, according to the World Database of Protected Areas. By clicking on an intersection shape, the name of the species is shown.



```{r}
interactive_map
```
