---
title: "Supplementary Data SD5"
output: html_document
---

<style>
.main-container {
    max-width: 2040px;
    margin-left: 10px;
    margin-right: auto;
}

</style>

<!-- https://stackoverflow.com/questions/57175174/how-to-remove-padding-on-left-side-of-r-markdown-generated-html-file -->

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE)
library(tidyverse)
library(DT)
```

```{r Data, include=FALSE}
species_list <- read_csv("data/full_species_list.csv") %>%
  rename(Countries= Countries...2,
         `Countries (PAs)` = Countries...16) %>% 
  mutate(`Distribution Area (km2)` =  format(`Distribution Area (km2)`, big.mark=","),
         `PA (km2)` =  format(`PA (km2)`, big.mark=","))


species_list_without_pa_names <- species_list %>% 
  mutate(Species = paste0('<em>',Species,'</em>'),
         `Conservation status (CS)` = as.factor(`Conservation status (CS)`),
         `Level of Threat` = as.factor(`Level of Threat`),
         `Population trend` = as.factor(`Population trend`),
         `Status revision` = as.factor(`Status revision`)) %>% 
  relocate(`Source (CS)`, .after = `Conservation status (CS)`) %>% 
  relocate(`Status revision`, .before = `Level of Threat`) %>% 
  select(-c(`PA names`,`Countries (PAs)`))

species_list_without_pa_names[species_list_without_pa_names == '<em>Iber치</em>'] <- 'Iber치'

```

```{r Tabla, echo=FALSE}
x = datatable(species_list_without_pa_names,
              escape=FALSE,
              rownames = FALSE,
              colnames = c('PA (Km<sup>2</sup>)' = 'PA (km2)',
                       'Natural cover 2020 (%)' = '% Natural cover 2020',
                       'Distribution Area (Km<sup>2</sup>)' = 'Distribution Area (km2)',
                       'Net Natural-seminatural change (Km<sup>2</sup>)' = 'Net Natural-seminatural change (Km2)'),
              extensions = 'FixedColumns',
          options = list(
            fixedColumns = list(leftColumns = 1)),
          filter = 'top') %>% 
  formatRound('Natural-seminatural cover 2000', 0) %>% 
  formatRound('Anthropic cover 2000', 0) %>% 
  formatRound('Natural-seminatural cover 2020', 0) %>% 
  formatRound('Anthropic cover 2020', 0) %>% 
  formatRound('Net Natural-seminatural change (Km<sup>2</sup>)', 0) %>% 
  formatRound('Natural cover 2020 (%)', 0) %>% 
  formatRound('Rate Natural-seminatural change (%)', 2)

```

## "Filling the gap in distribution ranges and conservation status in *Ctenomys* (Rodentia: Ctenomyidae)."
### *Caraballo, D. A., L칩pez, S. L., Botero-Ca침ola, S., and Gardner S. L.*

#### **Supplementary Data SD5**. Interactive table showing distribution areas, conservation status, overlap with protected areas, and habitat transformation in the past 20 years for 68 extant _Ctenomys_ species.

<br>
```{r, echo=FALSE}
x
```

